% This file uses the resume document class (res.cls)
% CV för Oscar Carlsson
\documentclass[11pt]{res} 
\setlength{\textheight}{9.5in} % increase text height to fit on 1-page 
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{hyperref}

\usepackage{fancyhdr}

\pagestyle{fancy}               % Fräcka sidhuvuden
\addtolength{\headwidth}{0cm}   % Sidhuvd bredare än texten.
\addtolength{\headheight}{24.8064pt}
\renewcommand{\headrulewidth}{0.4pt} % Linje i sidhuvud är 0.4 punkter
\renewcommand{\footrulewidth}{2pt} % Linje i sidfot är 2 punkter

\fancyhead[L]{{\leftmark FRÖDINGSGATAN 8A\\41672, GÖTEBORG}}	% Vänstertext i sidhuvud
\fancyhead[R]{\rightmark COSCAR@STUDENT.CHALMERS.SE\\0705-132253}	% Högertext i sidhuvud

\begin{document} 
$\:$ \\
\name{OSCAR CARLSSON\\~~~~~~~~~~~~ 901210\\[12pt] }     % the \\[12pt] adds a blank
				        % line after name                      
\begin{resume}

 \centerline{{ \Large Programmer and Machine Learning enthusiast}}
After graduating from Chalmers in June 2014 I'm looking for a full-time position at a company in the forefront of technology. I see myself working as a Software developer or data scientist anywhere in the world and value a workplace where i constantly learn new things and get to tech others.

\section{TECHNICAL SKILLS}          
\vspace{-0.1in}	
	\begin{tabbing}
		\hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
		{\bf Languages} \> Python { \small\textit{Working}}, Java { \small\textit{Working}}, Haskell { \small\textit{Novice}}, \\ \> Unix shell script { \small\textit{Novice}}, R { \small\textit{Novice}}, SQL { \small\textit{Novice}} \\
		{\bf Other} \> Unix { \small\textit{Working}}, Git { \small\textit{Working}}, Vim, Hadoop MapReduce.\\
		{\bf Methodologies} \> Agile, Scrum. 


	\end{tabbing}       

\section{EDUCATION}          
\vspace{-0.1in}	

	\begin{tabbing}
		\hspace{2.3in}\= \hspace{2.6in}\= \kill
		    M.Sc. Algorithms, Language and Logic, Chalmers Tekniska Högskola  \> \> 2012 - (2014)\\
\textit{Majored in Algorithms and Machine Learning/Statistics. Complete list of courses upon request}  \\
\textit{GPA: 4.63/5 } \\
%	        \textit{Good (Solid?) background for further Ph.D. studies in Computer Science}
	\end{tabbing}

\vspace{-45pt}

	\begin{tabbing}
		\hspace{2.3in}\= \hspace{2.6in}\= \kill 
	 	B.Sc. Computer Science, Chalmers Tekniska Högskola \> \> 2009 - 2012 \\
		\textit{Basic computer science with mathematics, computing and electronics. } \\
		\textit{}
	\end{tabbing}

\vspace{-45pt}

       \begin{tabbing}
       		\hspace{2.3in}\= \hspace{2.6in}\= \kill
   		Computer Science, Tullängskolan \> \> 2006 - 2009 
       \end{tabbing}

%%%%%%%%%%%%%%%%%%%%%%%%%%%% ARBETSERFARENHET   %%%%%%%%%%%%%%%%%%%%%%%%%%%%  
\section{BUSINESS EXPERIENCE}
\vspace{-0.1in}
\begin{tabbing}
 \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
 \bf {Master Thesis} \>Spotify, Stockholm \>Jan - Jun, 2014\\
	The topic is ``Cluster user session`` and focuses on finding patterns in how users consume \\ music. 
	It has a data mining approach in order to learn more about users. \\ 
	Techniques used is Python MapReduce-jobs and all data is preprocessed and \\ analyzed using Python.
\end{tabbing}
\vspace{-30pt}
\begin{tabbing}
 \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
 \bf {Street Team} \>Spotify, Göteborg \>April - Dec, 2013\\
	Me and another student were single responsible for marketing Spotify at Chalmers. \\ We organized activities such as Hackathons, Tech Talks and similar marketing events. \\
	The biggest event we helped with was Student TechFest \url{www.studenttechfest.se}
\end{tabbing}
\vspace{-30pt}
\begin{tabbing}
 \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
 \bf {Software developer} \>Spotify, Stockholm \> Jun - Aug, 2013\\
Internship within Technology and Test Automation/Quality Assistance-chapter.\\
Wrote a monitoring service in Python that reported number of network-requests sent by a test client. \\
Worked on a feature to enable real-time visualization in a browser of a on going test in the open source \\ project \url{http://graphwalker.org}
. Worked on a plugin (Java) that integrates Jenkins with Virtualbox.

 \end{tabbing}

\vspace{-30pt}

\begin{tabbing}
 \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
 \bf {Software developer} \>Ericsson, Göteborg \>1 Jun - 31 Dec, 2012\\
	Maintained a Drupal-based (PHP) testing tool. Dealt with backend in Python and Bash. Worked in a \\ agile team, using Scrum, consisting of 6 people. We used git as version control and reviewed code \\ through Gerrit. 
	%I learnt the importance of unit testing, and continued working alongside my studies until the year's end. 
\end{tabbing}
\newpage
%\vspace{-30pt}

	   \begin{tabbing}
		 \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
		 {\bf Customer Service} \>Transcom, Karlskoga    \>Jun - Aug, 2010\\
		 Telephone customer service at Tele2. Both service and sales experience. 
	   \end{tabbing}

\vspace{-30pt}     

	  \begin{tabbing}
		  \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
		  {\bf Software developer} \>Proffice, Örebro \>Project 2009\\
		  Developed a tool for customer management in ASP with a MS Access-database.
		  %The job was done as a consultant for Proffice and served as a school project.
		  %, for which I and three classmates were chosen by our teachers. 
%		  Utvecklade ett verktyg för fakturering och uppdragshantering på lager.
%		  Berörde programmering i ASP, \\ Microsoft Access/SQL och linjär algebra. Valdes ut från klassen av lärare.
	  \end{tabbing}
\section{PROGRAMMING PROJECTS}
\vspace{-0.1in}
	\begin{tabbing}
		\hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
	 	{\bf Reinforcement Learning Agent in a discrete environment} \>	\\
	 	Course:  Decision making under uncertainty                    \> 	\> 2013 \\
		RL-competition (link) influenced competition where we build a C++ Reinforcement Learning \\
		Agent that implemented the Sarsa($\lambda$) algorithm. Source code and report is found at \\ 
		\url{ http://github.com/Oscarlsson/RL-competition}
	 \end{tabbing}

%%%%%%%%%%%%%%%%%%%%%%%%%%%% KANDIDATARBETE   %%%%%%%%%%%%%%%%%%%%%%%%%%%%  
%\section{BACHELOR THESIS}
%\vspace{-0.1in}
\vspace{-30pt}     
	\begin{tabbing}
		\hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
	 	{\bf Bachelor Thesis: Professional, high performance intranet for CHARM} \>	\\
	 	Supervisor:  Christer Carlsson                    \> 	\> 2012 \\
		Developed a intranet in the PHP framework CodeIgniter with a MySQL-database. \\ Built it for a organization, CHARM, and had to work with specifications and communicate with \\ the customer.
		The thesis involved a comparsion of different web frameworks and their security \\ and efficiency aspects. 
	 \end{tabbing}

\section{NON-PROFIT EXPERIENCE}  
\vspace{-0.1in}	
	\begin{tabbing}
		\hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
		{\bf  Vice-chairman}, Datateknologsektionen Chalmers. \> \>	2012 - 2013\\
		Member of the board, responsible for our faculty's 30th anniversary celebration. \\ Am the representative for issues regarding the students' working environment for this year.
	\end{tabbing}
\vspace{-30pt}

	\begin{tabbing}
		\hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
		{\bf  Extracurricular activity}, Datateknologsektionen Chalmers. \> \>	2011 - 2012\\
		Responsible for everything related to the student pub. Worked in the bar \\ during pubs, held beer-tasting occassions to spread knowledge among students. \\ Took a lot of responsibility and pride in always trying to make people feel welcome and at ease. \\\\
 	.. and various IT-support and administrator roles
	\end{tabbing}

\section{OTHER}          
    {\bf Scholarship: Adlerbertska}, Chalmers Tekniska Högskola 2013. \\
    {\bf Scholarship: Good grades and good comradery}, Tullängskolan Örebro 2009. \\
    {\bf Driver's license} Swedish class B. 

Grades, school certificates and references from former employers will be provided upon request. 

\end{resume}
\end{document}
